\documentclass[defaultstyle,11pt]{thesis}

\usepackage{amssymb}		% to get all AMS symbols
\usepackage{amsmath}
\usepackage{braket}
\usepackage{float}
\usepackage{longtable}
\usepackage{subcaption}
\usepackage[utf8x]{inputenc}
\usepackage{graphicx}		% to insert figures
\usepackage{hyperref}		% PDF hyperreferences??

%%%%%%%%%%%%   All the preamble material:   %%%%%%%%%%%%

\title{Search for High Mass States Decaying to Tau Pairs with the CMS Experiment}

\author{A.~A.}{Johnson}

\otherdegrees{B.S., Carnegie Mellon University, 2011 \\
	      M.S., University of Colorado, 2013}

\degree{Doctor of Philosophy}		%  #1 {long descr.}
	{Ph.D.,  Physics}		%  #2 {short descr.}

\dept{Department of}			%  #1 {designation}
	{Physics}		%  #2 {name}

\advisor{Prof.}				%  #1 {title}
	{John P. Cumalat}			%  #2 {name}

\reader{Prof.~Kevin Stenson}		%  2nd person to sign thesis
\readerThree{Prof.~Steven Wagner}		%  3rd person to sign thesis

\abstract{  \OnePageChapter	% because it is very short

Two searches for heavy neutral resonances, $Z^{\prime}$s, decaying to back-to-back tau pairs are completed using the Compact Muon Solenoid experiment at the Large Hadron Collider. The first, based on data accumulated during the 2012 data-taking run at $\sqrt{s} = 8$ TeV, focuses on the fully-leptonic $\tau_e\tau_\mu$ channel, in which one tau decays to an electron and the other to a muon. The second, carried out during the 2015 run at $\sqrt{s} = 13$ TeV, includes four major decay channels: the $\tau_e\tau_\mu$ channel, the $\tau_e\tau_h$ channel (in which one tau decays to an electron and the other decays hadronically into a jet), the $\tau_\mu\tau_h$ channel (in which one tau decays to a muon and the other decays hadronically), and the $\tau_h\tau_h$ channel (in which both taus decay into jets). Each search employs a hybrid of background estimation strategies using both Monte Carlo simulation and data-driven methods. The presence of neutrinos in the decays necessitates the use of missing energy in the final mass calculation. In both searches, observed data is found to be in agreement with Standard Model expectation and no excesses are observed. Limits are placed on the $Z^{\prime}$ mass such that, if the $Z^{\prime}$ exists, its mass must be greater than 2.1 TeV.
	}

\dedication[Dedication]{	% NEVER use \OnePageChapter here.
	To my parents, Carl and Sharon Johnson. Without your constant love, support, and encouragement, none of this would have been remotely possible.
	}

\acknowledgements{	\OnePageChapter	% *MUST* BE ONLY ONE PAGE!

I have often remarked that the fact that anything ever gets done at CERN is a miracle. This does not come from a place of cynicism, but rather from my profound sense of amazement at the sheer number of moving parts that must come together in order to operate the collider, run the detectors, analyze the data, and produce trustworthy results. Particle physics at CERN is indeed a global undertaking, and it requires the focused collaboration of thousands of staff scientists, faculty, PhD students, undergraduates, postdocs, engineers, support staff, and administrators in order to move the wheels of science along. Without them, forward progress would be impossible. In a similar sense, there are many, many people in my life without whom completing a PhD would have been impossible (or at the very least substantially more unpleasant).

First and foremost, I am forever indebted to my parents, Carl and Sharon Johnson. From an extremely early age, they both placed the utmost importance on academic achievement. My father, paragon of patience, happily spent countless hours (usually after a long day at the office) helping me through my math homework, and consistently challenged me to think analytically and to value a technical education. My mother, in addition to making me a much, much better writer, impressed upon me the interpersonal skills and social intelligence that allowed me to flourish in a multinational environment like CERN. I also owe a great deal to my delightful little sister, Madeline. Without her constant, whimsical-yet-bizarre influence growing up, I would be much more boring person. Finally, thank you to my wonderfully-lovely girlfriend, Michelle, who made writing so much more bearable.

I cannot begin to express my gratitude towards the academic role models who helped mold me into a physicist. Thanks to Prof. Kunal Ghosh, who first lured me into the Carnegie Mellon physics department with brownies and a ridiculous laugh, and who cultivated my leadership skills through several student organizations. Thanks also to Prof. Jim Russ, my undergraduate advisor, who helped me through the grad school process and who fostered my love of high energy physics. I'm tremendously grateful to my supervisors at Argonne Lab: Sasha Paramonov, for showing me those first ropes, and Prof. Jimmy Proudfoot, whose letter of recommendation is without a doubt what got me into grad school. Sincere thanks to Eduardo Luiggi, my postdoc for the first few years of grad school. He was extremely patient with me, and guided me through literally every step of our 8 TeV analysis. This was absolutely critical in preparing me to do research on my own, and I am so, so grateful for the help. Eduardo, someday I will find you and someday I will get you to smile. I'm also very grateful to my BSM3G group members, who did an extraordinary job with the analyses presented here. In particular, thanks to Francesco Romeo, who helped me a great deal with tau ID \& reconstruction, to Andres Florez, without whom I would never have been able to figure out the limit tools, and especially to Prof. Alfredo Gurrola, who developed a large amount of the software framework used in our analyses and who was an endless source of friendly advice and encouragement. Thanks also to Annapaola de Cosa and Christian Veelken for their invaluable guidance throughout all my service work. Thanks to Prof. Kevin Stenson, for teaching me that first particle physics class way back in 2011 and for letting bounce all those CMSSW questions off him, and thanks to Prof. Oliver DeWolfe for his friendship and for his willingness to assist me with all things high energy theory. Finally, thanks also to Doug Johnson, whose tireless upkeep of the CU-HEP computing system, the backbone upon which all of this work rests.

There exists an ingrained stereotype of the miserable graduate student. I have never related to this, and I think the primary reason for that is my group of friends here in Colorado. I could not have asked for a more entertaining, supportive, and hilarious cohort of fellow grad students and I feel exceptionally lucky to have gone through this experience with each of them by my side. In no particular order, they are: Jamey Szalay, Yomay Shyur, Andy Missert, Liz Shanblatt, Cathy Klauss, Jack Houlton, Andrew Koller, Victor Colussi, Scott Johnson, Oscar Henriksson, Brian O'Callahan, Sara Campbell, Bob Peterson, Ben Pollard, Brad Dinardo, Teesa Christian, and Casey Gardiner. Thanks for the ski days, wine clubs, trips to the Hill, and innumerable nights of laughter at Holmes Place. 

Special thanks is also due to the CERN/Geneva contingent - a group of PhD students, postdocs, and undergrads from all over the world who made my time there unforgettable. Laser Kaplan, Prof. Rachel Yohay, Prof. Ted Kolberg, Charlie Mueller, Sarah Buss, Grace Brown, Matthias Weber, Maria Hoffman, Vytautas Vislavicius, Shannon Ruse, Sarah Charley, Evan Wolfe, Stany Sevova, Andrew Hard, Christine McLean, Kira Burt, Siyuan Sun, and Justin Pilot. Monday night trivia with Colonel Moutarde and Friday night shenanigans at Champs Frechet were an absolute blast, and I am going to sincerely miss the unwavering tradition that was 3:00 PM coffee in R1. Apologies are also due to Lindt \& Spr{\"u}ngli AG, who I am sure noticed a significant dip in revenues after my departure from Switzerland.

Finally, I am so unbelievably lucky to have had Prof. John Cumalat as an advisor. Research in experimental particle physics can be extremely frustrating, especially when the majority of one's collaborators are an ocean and eight time zones away. John was incredibly understanding of this, and worked tirelessly to get me the help I needed, to the point of sending me to CERN twice as well as to multiple schools and workshops. Indeed, John has been phenomenally supportive throughout my graduate research career, and his guidance and insights have truly taught me to think like a particle physicist. John, you are an outstanding advisor and friend. Thank you for everything.

	}

% \IRBprotocol{E927F29.001X}	% optional!

\ToCisShort	% use this only for 1-page Table of Contents

\LoFisShort	% use this only for 1-page Table of Figures
% \emptyLoF	% use this if there is no List of Figures

\LoTisShort	% use this only for 1-page Table of Tables
% \emptyLoT	% use this if there is no List of Tables

\extrafloats{100}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%       BEGIN DOCUMENT...         %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\input macros.tex
\input zprimeDefinitions.tex
%\input Introduction.tex
\input theory.tex
\input CMS.tex
\input strategy.tex
\input triggers.tex
\input samples.tex
\input recoObjectAndID.tex
\input muTau.tex
\input diTau.tex
\input diTauHad_ZtautauCR.tex
\input eTau.tex
\input eMu.tex
\input Systematics.tex
\input Results.tex
\input Lifetime.tex
\input Conclusion.tex

%%%%%%%%%   then the Bibliography, if any   %%%%%%%%%
\bibliographystyle{plain}	% or "siam", or "alpha", etc.
\nocite{*}		% list all refs in database, cited or not
\bibliography{refs}		% Bib database in "refs.bib"
%\input refs.bib
%%%%%%%%%   then the Appendices, if any   %%%%%%%%%
\appendix
%\input appendixA.tex
%\input appendixB.tex


\end{document}

