\section{Strategy}\label{sec:strategy}
%\textbf{Responsible: A. Gurrola, T. Kamon, F. Romeo} 

A $\tau$ lepton is the heaviest known lepton with a mass of 1.777 GeV/$c^2$ and a lifetime of $2.9\times10^{-13}$ seconds. Around one third of
all $\tau$ leptons decay to $e/\mu$, and the remainder decay into hadronic jets ($\tau_{h}$). 
In the latter case, a $\tau_{h}$ consists of one, three, or (rarely) five charged mesons usually accompanied by one or
more neutral pions.

%As the $\tau$ lepton decays to $e\overline{\nu}_e}\nu_{\tau}~(17.8\%)$, $\mu\overline{\nu}_\mu}\nu_{\tau}~(17.4\%)$, and hadrons +
%$\nu_{\tau}~(64.8\%)$ we will refer to these decays as the $e$ decay channel, $\mu$ decay channel, and the  $\tau_\textrmr{h}$ decay
%channel. 
We consider four distinct analyses for pairs of $\tau$ lepton decays, namely \emu ~(6.2\%), \etau ~(23.1\%), \mutau  ~(22.5\%), and
\ditauhad ~(42\%). We ignore the \EE and \MM channels due to the copious Drell-Yan
Z/$\gamma^*\rightarrow e^+e^-, \mu^+\mu^-$ production, although there is ongoing development of algorithms to discriminate prompt $e/\mu$ from $\tau$ lepton 
decays to light leptons which will be utilized with the 2016 data/analysis.

The overall strategy of the analysis is similar in all channels. 
In general, we identify events with two oppositely charged, nearly back--to--back objects. Because the $\tau\tau$ system decays with up
to four neutrinos, we expect to have missing transverse energy (\MET) present in the event. In contrast to \zprime searches in the
$e^+e^-$ and $\mu^+\mu^-$ channels, the visible \ditau mass does not produce a narrow peak due to the missing neutrinos.
Instead, we look for a broad enhancement in the \ditau$+$\MET invariant mass distribution consistent with new physics.  Our
selections maintain high efficiency for signal events, provide strong background suppression, and reduce the influence of systematic
effects.  

As \zditau is both background as well as an important validation signal our final selection requirements are such that by removing or
reversing just a few cuts we can obtain a clean sample of \zditau events. In order to ensure robustness of the analysis and our
confidence in the results, whenever possible we rely on the data itself to understand and validate the efficiency of reconstruction
methods as well as the estimation of the background contributions. For that purpose we define control regions with most of the
selections similar to what we use in our main search but enriched with events from background processes. Once a background enhanced
region is created, we measure selection efficiencies in those regions and  extrapolate to the region  where we expect to observe our
signal. In cases where a complete data--driven method is not possible we make use of scale factors, ratio between observed data events
and expected MC events in the background enhanced region to estimate the background  contribution in the signal region. Although each
individual channel could have its own set of requirements, we maintain, wherever possible, consistent definitions and selection
criteria  between channels.

To quantify the significance of any possible excess or set upper limits on the production rate, we perform a fit of the $m(\tau_{1},\tau_{2},\MET)$ mass 
distribution and employ the CL$_{s}$ technique to interpret the results in terms of the upper 95\% credibility level limits
for each channel. The joint limit is obtained by combining the posterior probability density functions (likelihood) and taking into
account correlation of systematic uncertainties within and across channels.

The structure of this note is as follows: Sections~\ref{sec:triggers} and~\ref{sec:samples} describes the data sets used in each analysis. 
Section~\ref{sec:recoID} provides a brief discussion of the reconstruction and identification of the objects used to reconstruct our  $\tau\tau$ 
pairs.
%, while Section~\ref{sec:commonSelection} describes the common selection across the four different channels.
Sections~\ref{sec:muTauhad}--\ref{sec:eMu} describe the specific selections and background extraction methods applied  to each
individual channel. In Sections~\ref{sec:systematics}--\ref{sec:results} we describe the statistical method used to extract 
the $95\%$ C.L. upper limits and the results of the analysis. 
%Finally, Section~\ref{sec:conclusions} summarizes the results and 
%overall sensitivity.
  
